Sketch of DP - Bayesian Inference

### 2018-07-17 main-sketch.tex
typo

\noindent Also, in previous works, the accuracy has been measured again with respect to
$\ell_1$ norm. That is, a lower bound has been given to
\[
  \Pr[|\alpha - \tilde\alpha| + |\beta - \tilde\beta |\geq \gamma ]
\]
where $(\alpha, \beta), (\tilde\alpha,\tilde\beta)$ are as  defined above.
In this work we will use a metric based on a different norm to compute the sensitivity
and provide guarantees on the accuracy. In particular we will consider a metric
over probability measures and not over the parameters that represent them.
Specifically, we will use the Hellinger distance, which for two beta distributions
$\boldsymbol{\beta}_1=\betad(\alpha_1, \beta_1), \boldsymbol{\beta}_2=\betad(\alpha_2, \beta_2)$ is defined as
\[
  \hellinger(\boldsymbol{\beta}_1, \boldsymbol{\beta}_2)\equiv
  \sqrt{1 - \frac{\betaf(\frac{\alpha_1 + \alpha_2}{2}, \frac{\beta_1 + \beta_2}{2})}{\sqrt{\betaf(\alpha_1,\beta_1)\betaf(\alpha_2,\beta_2)}}}
\]
The same change of metric will be applied to the experimental accuracy guarantees.
% \section{Technical Problem Statement}
% \label{sec_bayesInfer}
% The posterior belief about parameters $\xis$ is inferred from the
% group of sensitive data. Because it is usually published in form of a
% distribution, for example, $\betad(\alpha',\beta'), \cdots,$ itself
% can relieve a lot of information about sensitive data. So, the
% sensitive information we want to protect here is the posterior belief,
% i.e., $Pr(\xis | \dataobs)$, rather than just a sample drew from
% it\cite{foulds2016theory}. Then it will be better if we can use a
% distance over two distributions to measure the accuracy than a
% distance over just parameters or values when we are protecting a
% distribution, for instance, Hellinger distance in our paper. When we
% measure the accuracy between true posterior and protected posterior
% using Hellinger distance, it would be better we can have a protection
% mechanism based on Hellinger distance. However, current mechanisms are
% mainly based on $l_1$ norm by Laplace mechanism
% \cite{zhang2016differential} \cite{xiao2012bayesian}. That's why we
% design our exponential mechanism over Hellinger distance to protect
% the whole posterior distribution.

@@

\section{Our Approach - Exponential Mechanism with Smooth Sensitivity}
\label{sec_smoo}

% \subsection{Algorithm Setting up}
We define a new mechanism $\hexpmech(x)$ which is similar to the exponential mechanism where we use $\mathcal{R}$ as the set $\betaset$ of beta distributions with integer parameters summing up to $n+2$, as scoring function we use the Hellinger distance from $\bysinfer(x)$, i.e. $\hlg(\bysinfer(x),-)$, and we calibrate the noise to the smooth sensitivity~\cite{nissim2007smooth}. The only difference is in the sensitivity part, since now we use the smooth sensitivity.

>>>>

\noindent Also, in previous works, the accuracy has been measured again with respect to
$\ell_1$ norm. That is, a lower bound has been given to
\[
  \Pr[|\alpha - \tilde\alpha| + |\beta - \tilde\beta |\geq \gamma ]
\]
where $(\alpha, \beta), (\tilde\alpha,\tilde\beta)$ are as  defined above.
In this work we will use a metric based on a different norm to compute the sensitivity
and provide guarantees on the accuracy. In particular we will consider a metric
over probability measures and not over the parameters that represent them.
Specifically, we will use the Hellinger distance $\hellinger(\cdot,\cdot)$, which for two beta distributions
$\boldsymbol{\beta}_1=\betad(\alpha_1, \beta_1),$ and $\boldsymbol{\beta}_2=\betad(\alpha_2, \beta_2)$ is equal to
\[
  \hellinger(\boldsymbol{\beta}_1, \boldsymbol{\beta}_2)\equiv
  \sqrt{1 - \frac{\betaf(\frac{\alpha_1 + \alpha_2}{2}, \frac{\beta_1 + \beta_2}{2})}{\sqrt{\betaf(\alpha_1,\beta_1)\betaf(\alpha_2,\beta_2)}}}
\]
The same change of metric will be applied to the experimental accuracy guarantees.
% \section{Technical Problem Statement}
% \label{sec_bayesInfer}
% The posterior belief about parameters $\xis$ is inferred from the
% group of sensitive data. Because it is usually published in form of a
% distribution, for example, $\betad(\alpha',\beta'), \cdots,$ itself
% can relieve a lot of information about sensitive data. So, the
% sensitive information we want to protect here is the posterior belief,
% i.e., $Pr(\xis | \dataobs)$, rather than just a sample drew from
% it\cite{foulds2016theory}. Then it will be better if we can use a
% distance over two distributions to measure the accuracy than a
% distance over just parameters or values when we are protecting a
% distribution, for instance, Hellinger distance in our paper. When we
% measure the accuracy between true posterior and protected posterior
% using Hellinger distance, it would be better we can have a protection
% mechanism based on Hellinger distance. However, current mechanisms are
% mainly based on $l_1$ norm by Laplace mechanism
% \cite{zhang2016differential} \cite{xiao2012bayesian}. That's why we
% design our exponential mechanism over Hellinger distance to protect
% the whole posterior distribution.

@@

\section{Our Approach - Exponential Mechanism with Smooth Sensitivity}
\label{sec_smoo}
Given a prior distribution $\betad(\alpha, \beta)$, depending on the dataset $\dataobs$, the posterior distribution will be one in the following set:
$$
% \subsection{Algorithm Setting up}
We define a new mechanism $\hexpmech(x)$ which is similar to the exponential mechanism where we use $\mathcal{R}$ as the set $\betaset$ of beta distributions with integer parameters summing up to $n+2$, as scoring function we use the Hellinger distance from $\bysinfer(x)$, i.e. $\hlg(\bysinfer(x),-)$, and we calibrate the noise to the smooth sensitivity~\cite{nissim2007smooth}. The only difference is in the sensitivity part, since now we use the smooth sensitivity.
